\section{Relevant Experience}

%\cventry{Jan 2021 - present}{NEU PRL Lab}%
%{Northeastern University}%
%{}%
%{}%
%{Researcher
%\newline{Northeastern University Programming Research Laboratory (NEU PRL), advised by
%Prof. Arjun Guha. Researching programming language and systems tools for
%serverless computing.}
%\newline{\href{https://prl.ccs.neu.edu/}{{\color{navyblue}prl.ccs.neu.edu}}}%
%\newline{}
%}

\cventry{May 2019 - Jan 2021}{PLASMA Lab}%
{University of Massachusetts Amherst}%
{}%
{}%
{Researcher
\newline{Programming Languages and Systems at Massachusetts lab (PLASMA), advised by Prof.
Arjun Guha. Researching programming language and systems tools for serverless
computing.}
\newline{\href{https://plasma-umass.org/}{{\color{navyblue}plasma-umass.org}}}%
%\newline{}
}

\cventry{}{Talks \& Publications}{}{}{}{}
\small
\cvitem{}{
Emily Herbert and Arjun Guha. A Language-based Serverless Function
Accelerator. 2020.
[\href{https://arxiv.org/abs/1911.02178}{{\color{navyblue}preprint}},
\href{https://github.com/emilyaherbert/containerless}{{\color{navyblue}repo}}]
%\newline{}
}
\cvitem{}{
Emily Herbert. A Language-based Serverless Function Accelerator. \textit{Cornell
CAPRA Lab.} 2020.
[\href{https://emilyaherbert.github.io/talks/cornell_2020.pdf}{{\color{navyblue}slides}}]
\newline{}
}
\normalsize

\cventry{June 2018 - May 2019}{DREAM Lab}%
{University of Massachusetts Amherst}%
{}%
{}%
{Researcher
\newline{Data systems Research for Exploration, Analytics, and Modeling lab (DREAM),
advised by Prof. Peter Haas. Researching deep learning methods for simulation input
modeling.}
\newline{\href{http://dbgroup.cs.umass.edu/}{{\color{navyblue}dbgroup.cs.umass.edu}}}%
%\newline{}
}

\cventry{}{Talks \& Publications}{}{}{}{}
\small
\cvitem{}{
Wang Cen, Emily A. Herbert, and Peter J. Haas. NIM: Modeling and
Generation of Simulation Inputs via Generative Neural Networks. \textit{Winter
Simulation Conference.} 2020.
[\href{https://emilyaherbert.github.io/preprints/WSC2020.pdf}{{\color{navyblue}paper}}] \textbf{Best Contributed Theoretical Paper Finalist}
%\newline{}
}
\cvitem{}{
Emily A Herbert. NIM: Generative Neural Networks for Simulation Input Modeling.
\textit{SCS Summer Simulation Conference.} 2019.
[\href{https://emilyaherbert.github.io/talks/summer-sim_2019.pdf}{{\color{navyblue}slides}}]
%\newline{}
}
\cvitem{}{
Emily A Herbert, Wang Cen, and Peter J Haas. NIM: Generative Neural
Networks for Simulation Input Modeling. \textit{Summer Simulation
Conference.} 2019.
[\href{https://people.cs.umass.edu/~phaas/files/SSC2019.pdf}{{\color{navyblue}short paper}}]
\newline{}
}
\normalsize

\cventry{June 2017 – Aug 2017}{National Aeronautics and Space Administration
(NASA)}%
{Langley, VA}%
{}%
{}%
{NASA Internships, Fellowships, and Scholarships (NIFS) Intern
\newline{Contributed to the NASA Safeguard autonomous drone geofencing project.
Designed and implemented system for on-board flight control of GPS devices.
Refactored code from previous NASA flight missions to meet current mission
standards.}%
\newline{}
}

\cventry{June 2016 – Aug 2016}{General Electric (GE), Oil \& Gas}%
{Billerica, MA}%
{}%
{}%
{Information Technology Leadership Program (ITLP) Intern
\newline{Created asset tracking system for shop floor using RFID, Bluetooth LE,
and Raspberry Pi. Worked with the SAP enterprise resource management software to
automate EHSM compliance checks.}%
%\newline{}
}