\Section
{Work Experience}
{Work Experience}
{PDF:Work Experience}

\Entry
\textbf{University of Massachusetts Amherst},
Amherst, MA 
\dotfill
\textbf{\DatestampYMD{2018}{09}{15} -- present}
\Gap
Teaching Assistant
\begin{Detail}
    \SubBulletItem
    Assist in the Mathematical Foundation for Informatics course.
    \SubBulletItem
    Act as a resource for students for help with mathematical logic, set theory, and proof writing.
    \SubBulletItem
    Design and implement set operation visualization application to be used as a student educational tool.
\end{Detail}

\BigGap
\Entry
\textbf{Trinity University},
San Antonio, TX
\dotfill
\textbf{\DatestampYMD{2016}{08}{15} -- \DatestampYMD{2018}{05}{15}}
\Gap
Teaching Assistant
\begin{Detail}
    \SubBulletItem
    Assist in the Principles of Computer Science I, Principles of Computer Science II, and Introduction to Programming Logic courses.
    \SubBulletItem
    Act as a resource for students for help with Scala, ScalaFX, Akka, Java, JavaFX, and Greenfoot.
    \SubBulletItem
    Design, implement, and upkeep test server for student projects using Scala, Akka, and Actors.
    \SubBulletItem
    Monitor student progress, host office hours, meet with students by appointment, host exam review sessions.
    %\SubBulletItem
    %Create and grade extra credit problem sets.
\end{Detail}

\BigGap
\Entry
\textbf{National Aeronautics and Space Administration (NASA)},
Langley, VA
\dotfill
\textbf{\DatestampYMD{2017}{06}{15} -- \DatestampYMD{2017}{08}{15}}
\Gap
NASA Internships, Fellowships, and Scholarships (NIFS) Intern
\begin{Detail}
    \SubBulletItem
    Contribute to the NASA SAFEGUARD/SMART project.
    \SubBulletItem
    Design and implement system for on-board flight control of GPS devices.
    \SubBulletItem
    Refactor code from previous NASA flight missions to meet current mission standards.
\end{Detail}

\Entry
\BigGap
\textbf{General Electric (GE), Oil \& Gas},
Billerica, MA
\dotfill
\textbf{\DatestampYMD{2016}{06}{15} --
\DatestampYMD{2016}{08}{15}}
\Gap
Information Technology Leadership Program (ITLP) Intern
\begin{Detail}
    \SubBulletItem
    Create asset tracking system for shop floor using RFID, Bluetooth LE, and Raspberry Pi.
    \SubBulletItem
    Work with the SAP enterprise resource management software to automate EHSM compliance checks.
\end{Detail}