%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,letterpaper]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{emily} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[left=0.70in,right=0.70in,top=0.50in,bottom=0.45in,nohead,includefoot]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\usepackage{fontspec}

\definecolor{navyblue}{rgb}{0.0,0.0,0.52}

\setmainfont
[Path=./fonts/tinos/,
ItalicFont=Tinos-Italic,
BoldFont=Tinos-Bold,
BoldItalicFont=Tinos-BoldItalic]
{Tinos-Regular.ttf}

\newcommand{\UseSecondaryFont}{\fontspec
[Path=./fonts/gnu_free_font/,
ItalicFont=FreeSerifItalic,
BoldFont=FreeSerifBold,
BoldItalicFont=FreeSerifBoldItalic]
{FreeSerif.otf}}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Emily} % Your first name
\familyname{Herbert} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
%\address{123 Broadway}{City, State 12345}
%\mobile{(000) 111 1111}
%\phone{}
%\fax{(000) 111 1113}
\email{emilyherbert@cs.umass.edu}
\homepage{emilyaherbert.com}{emilyaherbert.com} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{\href{https://www.github.com/emilyaherbert}{{github.com/emilyaherbert}}}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}
\thispagestyle{fancy}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-2] % Dummy text
%\lipsum[4] % Dummy text

%\makeletterclosing % Print letter signature

%\newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\maketitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2018--present}{PhD in Computer Science}{The University of Massachusetts Amherst}{Amherst, MA}{}{}  % Arguments not required can be left empty
\cventry{2014--2018}{BS in Computer Science}{Trinity University}{San Antonio, TX}{}{}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Publications}

\cvitem{}{
\textbf{Emily A Herbert}, Wang Cen, and Peter J Haas. NIM: Generative Neural
Networks for Simulation Input Modeling. \textit{SCS Summer Simulation
Conference.} 2019.
[\href{https://people.cs.umass.edu/~phaas/files/SSC2019.pdf}{{\color{navyblue}paper}}]
}

%----------------------------------------------------------------------------------------
%	PREPRINTS SECTION
%----------------------------------------------------------------------------------------

\section{Preprints}

\cvitem{}{
\textbf{Emily Herbert} and Arjun Guha. A Language-based Serverless Function
Accelerator. 2019.
[\href{https://arxiv.org/abs/1911.02178}{{\color{navyblue}arxiv}}]
}

%----------------------------------------------------------------------------------------
%	CONFERENCE TALKS & POSTERS SECTION
%----------------------------------------------------------------------------------------

\section{Conference Talks \& Posters}

\cvitem{}{
Wang Cen, Peter J Haas, \textbf{Emily A Herbert}. NIM: Generative Neural
Networks for Simulation Input Modeling. \textit{INFORMS Winter Simulation
Conference.} 2019.
[poster, to appear]
\newline{}
}

\cvitem{}{
\textbf{Emily A Herbert}, Wang Cen, Peter J Haas. NIM: Generative Neural
Networks for Simulation Input Modeling. \textit{SCS Summer Simulation
Conference.} 2019.
[\href{https://github.com/emilyaherbert/talks/blob/master/summer-sim_2019/summer-sim_2019_talk.pdf}{{\color{navyblue}talk}}]
}

%----------------------------------------------------------------------------------------
%	SERVICE SECTION
%----------------------------------------------------------------------------------------

\section{Service}

\cvitem{}{2019 Winter Simulation Conference Poster Session Reviewer}

%----------------------------------------------------------------------------------------
%	AWARDS & SCHOLARSHIPS SECTION
%----------------------------------------------------------------------------------------

\section{Awards \& Scholarships}

\cventry{July 2019}{David W. Stemple Scholarship in Computing}%
{University of Massachusetts Amherst}%
{}%
{}%
{Provides support to a first-year graduate student in Computer Science pursuing
a Ph.D. in Systems research.
%\newline{}%
\newline{}
%Detailed achievements:
}

\cventry{May 2019}{UMass CICS Women’s Travel Grant}%
{University of Massachusetts Amherst}%
{}%
{}%
{Awarded to UMass CICS women to assist with conference travel expenses.
%\newline{}%
\newline{}
}

\cventry{May 2019}{UMass CICS Travel Grant}%
{University of Massachusetts Amherst}%
{}%
{}%
{Awarded to UMass CICS students to assist with conference travel expenses.
%\newline{}%
\newline{}
}

\cventry{April 2019}{PLISS Studentship}%
{}%
{}%
{}%
{Awarded to new programming languages and systems researchers to attend the 2019
Programming Languages Implementation Summer School (PLISS).
%\newline{}%
\newline{}
}

\cventry{Nov 2018}{PLMW and POPL 2019 Scholarship}%
{SIGPLAN}%
{}%
{}%
{Awarded to new programming languages researchers to attend the 2019 Programming
Languages Mentoring Workshop (PLMW) and Principles of Programming Languages
Conference (POPL).
%\newline{}%
\newline{}
}

\cventry{Mar 2018}{2018 UMass CICS Fellowship}%
{University of Massachusetts Amherst}%
{}%
{}%
{Awarded to an outstanding graduate student applicant within the UMass CICS
applicant pool.
%\newline{}\newline{}
}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Research Experience}

\cventry{May 2019 - present}{PLASMA Lab}%
{University of Massachusetts Amherst}%
{}%
{}%
{Programming Languages and Systems at Massachusetts lab (PLASMA), advised by Dr.
Arjun Guha. Researching programming languages tools for serverless computing.
\newline{\href{https://plasma-umass.org/}{{\color{navyblue}plasma-umass.org}}}%
\newline{}
}

\cventry{June 2018 - May 2019}{DREAM Lab}%
{University of Massachusetts Amherst}%
{}%
{}%
{Data systems Research for Exploration, Analytics, and Modeling lab (DREAM),
advised by Dr. Peter Haas. Researching deep learning methods for simulation input
modeling.
\newline{\href{http://dbgroup.cs.umass.edu/}{{\color{navyblue}dbgroup.cs.umass.edu/}}}%
%\newline{}
}

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Teaching Experience}

\cventry{Sep 2018 - May 2019}{University of Massachusetts Amherst}%
{Amherst, MA}%
{}%
{}%
{Programming Methodology, \textit{Teaching Assistant}
\newline{Mathematical Foundation for Informatics, \textit{Teaching Assistant}}%
\newline{}
}

\cventry{Aug 2016 - May 2018}{Trinity University}%
{San Antonio, TX}%
{}%
{}%
{Principles of Computer Science II, \textit{Teaching Assistant}
\newline{Introduction to Programming Logic, \textit{Teaching Assistant}}%
\newline{Principles of Computer Science II, \textit{Teaching Assistant}}%
%\newline{}
}

%----------------------------------------------------------------------------------------
%	INTERNSHIP EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Internship Experience}

\cventry{June 2017 – Aug 2017}{National Aeronautics and Space Administration
(NASA)}%
{Langley, VA}%
{}%
{}%
{NASA Internships, Fellowships, and Scholarships (NIFS) Intern
\newline{Contributed to the NASA Safeguard autonomous drone geofencing project.
Designed and implemented system for on-board flight control of GPS devices.
Refactored code from previous NASA flight missions to meet current mission
standards.}%
\newline{}
}

\cventry{June 2016 – Aug 2016}{General Electric (GE), Oil \& Gas}%
{Billerica, MA}%
{}%
{}%
{Information Technology Leadership Program (ITLP) Intern
\newline{Created asset tracking system for shop floor using RFID, Bluetooth LE,
and Raspberry Pi. Worked with the SAP enterprise resource management software to
automate EHSM compliance checks.}%
%\newline{}
}

%----------------------------------------------------------------------------------------
%	RELEVANT COURSEWORK SECTION
%----------------------------------------------------------------------------------------

\section{Relevant Coursework}

\cventry{}{Completed at University of Massachusetts Amherst}%
{}%
{}%
{}%
{Programming Languages, Programming Languages Seminar, Systems, Research
Methods%
\newline{}
}

\cventry{}{Completed at Trinity University}%
{}%
{}%
{}%
{Computer Science Thesis I \& II, Programming Languages, Operating Systems, Big
Data, Software Engineering, Principles of Functional Languages, Theoretical
Computer Science, UNIX Power Tools, Principles of Computer Design, Data
Abstraction, Game Theory, Discrete Data Structures, Linear Algebra, Competitive
Programming
\newline{}
}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

%\section{Awards}

%\cvitem{2011}{School of Business Postgraduate Scholarship}
%\cvitem{2010}{Top Achiever Award -- Commerce}

%----------------------------------------------------------------------------------------

\end{document}